A publishing infrastructure for AI-assisted academic authoring

### 2023-07-11 latex/manuscript.tex
conclusions: mention custom prompts

We implemented AI-based revision models into the Manubot publishing platform.
Writing academic papers can be time-consuming and challenging to read, so we sought to use technology to help researchers communicate their findings to the community.
Our AI-based revision workflow uses a prompt generator that creates manuscript- and section-specific instructions for the language model.
Authors can easily trigger this workflow from the GitHub repository to suggest revisions that can be later reviewed.
This workflow uses GPT-3 models through the OpenAI API, generating a pull request of revisions that authors can review.
We set default parameters for GPT-3 models that work well for our use cases across different sections and manuscripts.
Users can also customize the revision by selecting specific sections or adjusting the model's behavior to fit their needs and budget.
Although the evaluation of the revision tool is subjective, we found that most paragraphs were improved.
The AI model also highlighted certain paragraphs that were difficult to revise, which could be challenging for human readers too.

>>>>

We implemented AI-based revision models into the Manubot publishing platform.
Writing academic papers can be time-consuming and challenging to read, so we sought to use technology to help researchers communicate their findings to the community.
Our AI-based revision workflow uses a prompt generator that creates manuscript- and section-specific instructions for the language model.
Authors can easily trigger this workflow from the GitHub repository to suggest revisions that can be later reviewed.
This workflow uses GPT-3 models through the OpenAI API, generating a pull request of revisions that authors can review.
We set default parameters for GPT-3 models that work well for our use cases across different sections and manuscripts.
Users can also customize the revision by selecting specific sections, adjusting the model's behavior to fit their needs and budget, and even providing custom prompts instead of using the default, section-specific ones, which can be useful for specific use cases that do not require a complex revision.
Although the evaluation of the revision tool is subjective, we found that most paragraphs were improved.
The AI model also highlighted certain paragraphs that were difficult to revise, which could be challenging for human readers too.
